\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Resize Figure 6

<!--prediction for true-model of S-curve-->
::: {#fig-scurve-pred-sc layout-ncol="2" fig-pos="H"}
![](figures/scurve/sc_true_only.png)

![](figures/scurve/pred_true_view.png)

>>>>

<!--prediction for true-model of S-curve-->
::: {#fig-scurve-pred-sc layout-ncol="2" fig-pos="H"}
![](figures/scurve/sc_true_only.png){width="150" fig-align="center"}

![](figures/scurve/pred_true_view.png){width="150" fig-align="center"}

### 2024-07-04 paper.tex
Resize Figure 6

\begin{minipage}{0.50\linewidth}
\includegraphics{figures/scurve/sc_true_only.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/scurve/pred_true_view.png}\end{minipage}%

>>>>

\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_only.png}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/pred_true_view.png}
\end{center}
\end{minipage}%
